---
title: "clase 10 de septiembre"
author: "maria de jesus juarez martinez"
output: html_document
date: "2025-09-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```{r}
discriminante <- function(a, b, c) {
  soluciones <- b^2 - 4*a*c
  if (soluciones < 0) {
    resp <- "No hay solución"
  } else {
    resp <- "Sí hay solución"
  }
  return(list(respuesta = resp, valor = soluciones))
}
intento1 <- discriminante(5, 2, 3)
intento1
```

#---matriz---
```{r}
# Vectores para la matriz
valores <- c(15, 13, 8, 3, 27, -4, -2, 10, 11)
A <- matrix(valores, nrow = 3, byrow = TRUE)

# Transpuesta
tA <- t(A)

valores2 <- c(15, 3, -2, 13, 27, 10, 8, -4, 11)
A2 <- matrix(valores2, nrow = 3, byrow = TRUE)

# Vector columna b
b <- matrix(c(-3, 2, -1), nrow = 3)

# Matrices aumentadas
Ab <- cbind(A, b)
bA <- cbind(b, A)
abt <- rbind(A, t(b))
btA <- rbind(t(b), A)

r1<-Ab[1,]
r2<-Ab[2,]
r3<-Ab[3,]
c1<-Ab[,1]
c2<-Ab[,2]
c3<-Ab[,3]
a11<-Ab[1,1]
a22<-Ab[2,2]
a32<-Ab[3,2]
a23<-Ab[2,3]
a14<-Ab[1,4]
a24<-Ab[2,4]
m1=-Ab[2,1]/Ab[1,1]
m2<- -Ab[3,1]/Ab[1,1]
A1<-Ab[1,]
A2<-m1*Ab[1,]+Ab[2,]
A3<-m2*Ab[1,]+Ab[3,]
m3<-(-Ab)[3,2]/Ab[2,2]
A3<-m3*Ab[2,]+Ab[3,]

# Mostramos resultados
A; tA; A2; b; Ab; bA; abt; btA
```